

# Introduction {#intro}

## THE CHALLLENGER.{#challenger}

If you have ever been in a data analytics class I bet you have ever heard of [Edward Tufte](https://www.tufte.com). On his criticisms on the engineers' failures to make sense of the concerns the had on lunching [The Challenger](https://www.nasa/challenger/.com) on January 28, 1986.
```{r , include=F}
xfun::embed_file(path = "/home/rwills/Rproject/REPORTS MADE EASY/TUFTE/Tufte.pdf",name = "The Challenger", text = "Download Tuftes' Challenger Cristisms")
```

>Being Right isn't enough, you have to be convincing.
>
>
> ~ Edward Tufte

This philosophy formed the basis of his arguments in his book _Visual Explanations and Quantities, Evidence and Narrative_

>An essential analytic task in making decisions based on evidence
is to understand how things work—mechanism, trade-offs, process
and dynamics, cause and effect. That is, intervention-thinking and
policy-thinking demand causality-thinking

>Making decisions based on evidence requires the appropriate display
of that evidence. Good displays of data help to reveal knowledge
relevant to understanding mechanism, process and dynamics, cause
and effect. That is, displays of statistical data should directly serve the
analytic task at hand.


Hence we are going set our reports right even before we begin in whatever we are supposed to report on.


## DATA {#data}
Lets take an hypothetical data where in Africa the distance students take to walk to get access to basic education affect their perfomance.

```{r data,}
set.seed(123)
n <- 30
df <- tibble(
  score=sample(30:99, size = n, replace = T),
  dist=sample(1:8, size=n, replace = T)
)

head(df)#Checking the first six observations

### Any time you get data into your hands always check its health status ie, the first thing you get in a hospital is checking weight, height, BMI, blood pressure etc.
### 
### Height & Weight
nrow(df)#number of rows
ncol(df)#number of columns
### Pressure
str(df)#structure
### BMI
dim(df) 
colnames(df)
### 
```
