# EXPLANATORY DATA ANALYSIS {#eda}
Here we form the foundation of our report. We listen to what the data has for us.This should be the entry step in a data project, where we start by knowing the correct data types and exploring distributions in numerical and categorical variables.
Always getting your data into the right format will affect how you work with them hence inferences that they generate.

At this point we perform dataset _'anatomy'_ namely;

        *Getting metrics like total rows, columns, data types, zeros, and missing values
        *How each of the previous items impacts on different analysis
        *How to quickly filter and select variables.
        
        *Univariate analysis in categorical variable:
           
           +Frequency, percentage, cumulative value, and colorful plots
        *Univariate analysis with numerical variables:
           +Percentile, dispersion, standard deviation, mean, top and bottom values
          +Plotting distributions

Based on our \@ref(data) we can develop the following questions.
  
    *Can we divide the perfomance into fail and passed?
    *What distance community does one above categories fall into?
    
## DATA WRANGLING {#dw}

```{r wrangling}
df$performance <- fifelse(df$score>=40, yes = "passed", no="failed") #answering the first question.
df$dist_comm <- fifelse(df$dist<=1, yes = "near",
                        fifelse(df$dist>1 & df$dist<=4,
                                yes="average",
                                no="far")
                        )#answering the second question.
df$dist <- as.factor(df$dist)
df$dist_comm <- as.factor(df$dist_comm)
df$performance <- as.factor(df$performance)
```

## Visualization {#vis}

```{r visBox-fig, fig.align='center',out.width='80%', fig.cap="boxplot of score based pn distance students walk"}
df %>% 
  ggplot(aes(dist, score))+
  geom_boxplot()+
  labs(title = "BOXPLOT OF STUDENTS'\nSCORE BASED ON DISTANCE.")

```
Its results above is astonishing, for see students in coming from distance 3-4 perform even better than those who are close to school.

```{r visBar-fig, fig.cap='Bargraphs of students score perfomance based on different factors.', fig.align='center'}
df %>% 
  ggplot(aes(y=score, fill=performance))+
  geom_bar(position = "stack")+
  facet_wrap(~performance)+
  labs(title = "Bargraph OF STUDENTS'\nSCORE.")

df %>% 
  ggplot(aes(y=score, fill=performance))+
  geom_bar(position = "identity")+
  facet_wrap(~dist_comm)+
  labs(title = "Bargraph OF STUDENTS'\nSCORE. IN DIFFERENT DISTANCE COMMUNITIES")

```


